---
title: "<span style = 'font-size: 100%;'> MGMT 17300: Data Mining Lab </span>"
subtitle: "<span style = 'font-size: 150%;'> Intro. & Technical Enablers </span>"
author: "Professor: Davi Moreira"
date: "2024-08-01"
date-format: "MMMM DD, YYYY"
format:
  revealjs: 
    transition: slide
    background-transition: fade
    width: 1600
    height: 900
    center: true
    slide-number: true
    incremental: true
    chalkboard: 
      buttons: false
    preview-links: auto
    #logo: images/quarto.png
    footer: "Data Mining Lab"
    theme: [simple,custom.scss]
---

# XXXX {background-color="#cfb991"}

## Overview

::: nonincremental
::: columns
::: {.column width="50%" style="text-align: center; justify-content: center; align-items: center;"}
-   XXX
-   XXX

:::

::: {.column width="50%" style="text-align: center; justify-content: center; align-items: center;"}
-   XXX
-   XXX
:::
:::
:::

### Importing Data

As we mentioned when discussing projects in `RStudio`, an excellent package for navigating the project directory is the `here` package.

The function that gives the package its name is used to direct your program to the correct folder in the project directory. Let's see an example:

```{r eval=FALSE, echo=TRUE}

if(!require(tidyverse)) {install.packages("tidyverse"); require(tidyverse)}
if(!require(here)) {install.packages("here"); require(here)}

cnj <- read_csv2(here("data/tribunais_despesa_2019_cnj.csv"))
```

### Exporting Data

Suppose that after you load the dataset, you perform tasks that change its configuration, and you want to save it without overwriting the original dataset.

```{r eval=FALSE, echo=TRUE}
write_csv2(cnj, here("data/tribunais_despesa_2019_cnj_filter.csv"))
```

# Summary {background-color="#cfb991"}

## Summary

::: nonincremental
-   **Modern Data Driven Decision Making (M3DM)**:

    -   M3DM is essential in leveraging data to guide business decisions.
    -   The approach integrates statistics, machine learning, and data management to inform and optimize strategies.

-   **Technical Pillars**:

    -   **Data Acquisition**: Gathering relevant and high-quality data.
    -   **Data Processing**: Cleaning, transforming, and organizing data for analysis.
    -   **Data Analysis**: Using statistical and machine learning techniques to extract insights.

-   **Practical Application**:

    -   Real-world applications of M3DM include predictive analytics, customer segmentation, and operational optimization.
    -   Data-driven decisions can significantly enhance business performance and competitive advantage.
:::

# Thank you! {background-color="#cfb991"}
